Title

### 2024-06-10 paper/main.tex
Updates

To compare how well does creating a graph manually based on effect sizes and
p-value compare to algorithmic approaches, we performed some empirical
analysis.

\subsection{Simulating an expert}
To simulate an expert building a model manually, we wrote a simple greedy simulation as shown in the Figure. The expert always starts with a graph with
no edges and chooses the pair of variables with the highest correlation between them. The expert based on some accuracy measure decides the direction
of the edge between these variables such that the new added edge does not create a cycle in the DAG.

\todo[inline]{Summarize this section and equation in an algorithm}
\todo[inline]{Show a consistency proof for this expert simulation}

@@

% \begin{algorithm}
% 	\caption{Expert Simulation}
% 	\While{True}{
% 	   $ e \gets \textnormal{Effects}(G) > \textnormal{THRESHOLD} $\;
% 	   $ e \gets e - \textnormal{blacklist} $\;
% 	   \If {$ e = 0 $}{
% 		$ G \gets G - e $ \;
% 		$ \textnormal{blacklist} \gets \textnormal{blacklist} \cup e $\;
% 	   } \;
% 	   \If{$ \textnormal{len}(e) = 0$}{
% 		   $ \textnormal{return}(G) $\;
% 	   }
% 	   $ X, Y \gets \max_{X, Y} e $\;
% 	   $ dir \gets Expert(X, Y, \alpha) $\;
% 	   $ G \gets G \cup dir $\;
% 	}
% 
% \end{algorithm}

After adding each edge, we also check if the p-value of any existing edge shows independence. If that happens we remove that edge and blacklist that edge. 
Blacklisted edges are not suggested to the expert in future iterations. We repeat this till we have explained all the correlations in the dataset.

There is a possibility that this greedy expert gets stuck at incorrect graph structures as it does not do any backtracking to fix its earlier mistakes.

>>>>

To compare how well this manual appraoch assisted by the suggested modications
perform compared to automated learning algorithms, we performed an analysis
using simulated data and simulating an expert. To construct the model using
suggestions, we start with a model with no edges, and take a greedy approach
for adding edges. At any point, we select to add an edge between variables that
have the highest conditional association between them. A simulated expert is
then asked to specify the direction for the edge. Given an accuracy of the
expert $ \alpha $, the expert either gives the correct direction, incorrect
direction, or can specify do not know as:

@@

If the expert says `do not know` for any of the edges, the edge is not prompted
again to the expert. We also make sure that only edges which do not form a
cyclic in the graph are used to select the next potential edge. After adding
each edge, we also check if the p-value of any existing edge shows
independence. If that happens we remove that edge and blacklist that edge,
i.e., that edge is not prompted again during the run of the algorithm. We
repeat this procedure till the model explains all correlations between the
variables. There is a possibility that this greedy expert gets stuck at
incorrect graph structures as it does not do any backtracking to fix its
earlier mistakes. This procedure is outlined in the Algorithm.
\todo[inline]{Add the algorithm}
